Figures

### 2020-01-07 manuscript/figures.Rmd
add proportion maxdepth by state fig

```{r maps, fig.cap = "Map of lake maximum depth in the continental United States.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/00_map-1.pdf")
```

>>>>

```{r maps_dot, fig.cap = "Map of lake maximum depth in the continental United States.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/00_map-1.pdf")
```

```{r maps_state, fig.cap = "Proportion of lakes greater than 4ha with maximum depth availability by state.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/00_map_state-1.pdf")
```
